### 2017-07-18 README.Rmd
Implemented one mean hypothesis test
Add one median bootstrap CI and hypothesis test

@@

>>>>

One numerical variable (mean)

```
mtcars %>%
  specify(response = mpg) %>% # alt: mpg ~ NULL (or mpg ~ 1)
  hypothesize(null = "point", mu = 25) %>% 
  generate(reps = 100, type = "bootstrap") %>% 
  calculate(stat = "mean")
```

One numerical variable (median)

```
mtcars %>%
  specify(response = mpg) %>% # alt: mpg ~ NULL (or mpg ~ 1)
  hypothesize(null = "point", Med = 26) %>% 
  generate(reps = 100, type = "bootstrap") %>% 
  calculate(stat = "median")
```

@@

One numerical (one median)

```
mtcars %>%
  specify(response = mpg) %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "median")
```
